Approximation as Differentiation: Notes

### 2025-07-03 notes/stable-coproducts.tex
First pass over stable coproducts.

Important to the idea of an extensive category is how coproducts behave under composition with an arbitrary
morphism. This is an instance of the notion of stability of colimits (in this case, coproducts) under
pullback or change of base.

>>>>

Important to the idea of an extensive category is how coproducts behave under composition with an arbitrary
morphism. This is an instance of the notion of stability of colimits (in this case, coproducts) under pullback
or change of base. Suppose $\cat{C}$ a category with coproducts $(\coprod, 0)$. The coproducts of $\cat{C}$
are \emph{stable under pullback} if for every object $X \iso X_1 \coprod X_2$ and morphism $g: Y \to X$, there
exists an object $Y \iso Y_1 \coprod Y_2$ and morphisms $h_1: Y_1 \to X_1$ and $h_2: Y_2 \to X_2$ such that
the following diagram commutes for every $i \in \{1, 2\}$,:

\begin{center}
\begin{tikzcd}
   & Y \arrow[rd, "g"] \\
   Y_i \arrow[rd, "h_i"'] \arrow[ru, "\inMap_i"] && X \\
   & X_i \arrow[ru, "\inMap_i"']
\end{tikzcd}
\end{center}
